---
title: "Project_2"
author: "James Muguira, D.M."
date: "05/23/2015"
output: html_document
---

# Overview

The length of tooth growth in 10 guinea pigs is tested for 3 dose levels of vitamin C (0.5, 1, and 2 mg).  The vitamin C is delivered using 2 methods: orange juice and ascorbic acid

# Initial setup

```{r}
library(datasets)
data(ToothGrowth)
str(ToothGrowth)

#
# Notice that dose is numeric, convert that to factor for analysis
ToothGrowth$dose <- as.factor(ToothGrowth$dose)
head(ToothGrowth)
```

Where

* len = numeric: tooth length

* supp = factor: supplement type (VC or OJ)

* dose = factor: dose in milligrams


# Explore the data graphically

Show boxplots, which display the minimum, 1st quartile, median, 3rd quartile and maximum.

* 1st, investigate the dosage:

```{r}
library(ggplot2)

ggplot(aes(x=dose, y=len), data=ToothGrowth) + geom_boxplot(aes(fill=dose))
```

* 2nd investigate delivery method:
```{r}
ggplot(aes(x=supp, y=len), data=ToothGrowth) + geom_boxplot(aes(fill=supp))
```

# Hypthesis testing and confidence intervals

* Test 1

The null hypthesis = different delvery method has no effect on tooth length

The alternate hypthosis = different delivery method has a effect on tooth length

```{r}
t.test(len ~ supp, data=ToothGrowth)
```

* Result

Given the small p-value and the fact that the confidence interval contains zero I would say the delivery method does not effect tooth growth (can not reject the null hypothesis)

* Test 2

The null hypthosis = different dosage level has no effect on tooth growth

The alternate hypothesis = different dosage level does effect tooth growth

```{r}
# first let's split up and compare each dose level range
tg0.5_1.0 <- subset(ToothGrowth, dose %in% c(0.5, 1.0))
tg1.0_2.0 <- subset(ToothGrowth, dose %in% c(1.0, 2.0))
tg0.5_2.0 <- subset(ToothGrowth, dose %in% c(0.5, 2.0))

t.test(len ~ dose, data=tg0.5_1.0)
t.test(len ~ dose, data=tg1.0_2.0)
t.test(len ~ dose, data=tg0.5_2.0)

```

* Result

All 3 t tests have very small p-values and none of the confidence intervals contain zero.  This indicates we can reject the null hypothesis (dose level does not effect tooth growth rate).  This would indicate that the dose level does effect tooth growth.

# Assumptions

* The tests were unpaired

* The sample guinea pigs were basically the same size and weight, and thus the results are generalizable


