---
title: "Statistical Inference Project 1"
author: "James Muguira, D.M."
date: "05/24/2015"
output: html_document
---

# Overview

In this project we have been asked to investigate the exponential distribution by comparing it with the Central Limit Theorem.  We will use R and simulate the distribution through this R form:

rexp(n, lambda)

Where:

* Lambda is the rate

* n is the number of exponentials 

* mean of the exponential distribution is 1 / lambda

* Standard Deviation for the exponential distribution is 1 / lambda.

For this investigation lambda is fixed at 0.2 for all trials. We investigate the averages of 40 exponentials and we run a 1000 replications.

This investigation will answer cover 3 areas:

* 1.  Compare the sample and theoretical mean of the distribution

* 2.  Compare the theoretical and sample variance of the distribution

* 3.  Show that the exponential distribution is approximately normal.

# Initial setup

set up the variables and generate a set of data to work with.  

```{r}
numberOfSimulations <- 1000
n <- 40
lambda <- 0.2
set.seed(1234)
data <- matrix(rexp(numberOfSimulations * n, rate=lambda), numberOfSimulations)
# take the mean or average of the generated data
data_mean <- apply(data, 1, mean)
```

# Sample Mean verses Theoretical Mean

```{r}
theory_mean <- 1/lambda
theory_mean
simulatedDistribution_mean <- round(mean(data_mean), 3)
simulatedDistribution_mean
```

# Sample Variance verses Theoretical Variance

```{r}
samVariance <- round(var(data_mean), 3)
samStDev <- round(sd(data_mean), 3)

theoryVariance <- round(((1/lambda)^2)/n, 3)
theoryStDev <- round((1/lambda)/sqrt(n), 3)


```

Use a table to gather the theoretical and sample means, variances and standard deviations together to make comparing easier.

```{r}
df <- rbind(c(simulatedDistribution_mean, samVariance, samStDev), c(theory_mean, theoryVariance, theoryStDev))

row.names(df) <- c("Sample", "Theoretical")
colnames(df) <- c("Mean", "Variance", "Stand Dev")
df
```

# Distribution Approximately Normally Distributed?

Does a histogram of the data look normal?

```{r}
hist(data_mean, main="Distribution of averages")
```

The histogram looks close to normal.  However, utilizing a Q-Q plot will tell us more.

```{r}
qqnorm(data_mean); qqline(data_mean)
```

The Q-Q Plot shows that the exponential distribution is approximately normal, except in the tails.