---
title: "Statistical Inference Project 1"
author: "James Muguira, D.M."
date: "05/20/2015"
output: html_document
---

Synopsis

Overview


```{r}
library(ggplot2)
numOSim <- 1000
n <- 40
lambda <- 0.2
set.seed(1234)
data <- matrix(rexp(numOSim * n, rate=lambda), numOSim)
data_mean <- apply(data, 1, mean)
hist(data_mean)
```

Now, compare the simlated distribution to the theoretical distribution.


Sample Mean verses Theortical Mean

```{r}
theory_mean <- 1/lambda
theory_mean
simDist <- round(mean(data_mean), 3)
simDist
```


```{r}
dataDF <- data.frame(data_mean)
grph <- ggplot(dataDF, aes(x=data_mean))
grph <- grph + geom_histogram(aes(y=..density..))
grph + geom_density(colour="red", size=1)
```

How well does the 
Now, analyize the theoretical and simulation and distribution variance

Sample Variance verses Theoretical Variance

```{r}
theoryVar <- round(((1/lambda)^2)/n, 3)
theorySD <- round((1/lambda)/sqrt(n), 3)
theoryVar
theorySD
```

Does the exponential distribution approximate a normal distribution?

Distribution Approximately Normally Distributed?